\documentclass[10pt, a4paper]{moderncv}

\linespread{1.4}

\usepackage{url}


% colors: black, blue, green, grey, orange & purple
% styles: banking, casual, classic & oldstyle
\moderncvtheme[grey]{classic}

% character encoding
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{datetime}

\newcommand{\revision}{\twodigit\day\twodigit\month\the\year}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[RE, RO]{\footnotesize{rev. \revision}}

% adjust the page margins
\usepackage[scale=.80]{geometry}
\setlength{\hintscolumnwidth}{3cm}
\AtBeginDocument{\recomputelengths}

% personal data
\firstname{Ivan}
\familyname{Pedrazas}
\mobile{+44 74 2934 XXXX}
\homepage{blog.pedrazas.me}
\email{ipedrazas@XXXXX.com}

\begin{document}
\maketitle


%
% PROFESSIONAL EXPERIENCE
%

\section{Core Skill Base}
\cvline{}{Passionate, creative, pragmatic and very pro-active software engineer
with a strong focus on designing and building solutions. Natural team leader,
 who enjoys mentoring.}

\cvline{}{Very comfortable being a bridge between Business and Technical teams
with many years of experience dealing with Enterprise Application Integration
and Business and Content Architecture.}

\cvline{}{Full stack person able to design, develop, test and deploy and
administer complex solutions based on distributed architectures.}

\cvline{}{For the last 6 months I've been very focused on improving the
experience of building and deploying immutable architectures based on kubernetes.}

\cvline{}{}

\section{Professional experience}

\cventry{Apr. 2016 -- Curr}
{Senior DevOps Engineer}
{Contino ltd.}{UK}{}
{Productionizing Kubernetes running on VMWare for BSkyB.
Defined the different kubernetes modules and helped to
provision a cluster with TLS and tokens.
Showcase, configure and deploy Prometheus.
Helped to onboard a CMS project to the kubernetes cluster.
Created a series of screencasts about kubernetes.
\\}

\cvline{}{}

\cventry{Sept 2015--Apr. 2016}
{Principal Consultant}
{UK Home Office}{UK}{}
{Helped to onboard different projects in the different Kubernetes clusters.
Designed and implemented part of the CI/CD pipelines based on jenkins and drone.
Contributed to building the HomeOffice Digital platform based on kubernetes,
hashicorp Vault, Keycloak on AWS.\\}

\cvline{}{}

\cventry{April 2015--July 2015.}
{Senior DevOps Engineer}
{Import.io ltd.}{UK}{}
{Refactored provisioning strategy to use docker and replace the building and
packaging process based on AWS AMIs.
Design of an application based on micro services to manage dockerized infrastructure.
Refactored data services to use eventual consistency based on Apache Kafka.\\}

\cvline{}{}

\cventry{Nov 2014--April 2015.}
{Senior Big Data DevOps Engineer}
{Adbrain ltd.}{UK}{}
{Designed a strategy called  ``Agile Clusters'' that reduce Infrastructure costs \textbf{by 30\%}. Developed an application based on microservices running in Docker to manage Apache Spark and Apache Cassandra clusters and orchestrate Adbrain's cloud infrastructure based on Amazon AWS and Azure. Refactored the deployment methodology, redefined how to create Continous Deployment using Jenkins, Docker and Chef.\\}

\cvline{}{}


\cventry{Nov 2010--Aug 2014}
{Software Architect}
{European Medicines Agency}{UK}{}
{Defined and implemented the Records Managament Roadmap according to the enterprise guidelines to fullfill the Life Sciences requirements. Evaluation and implementation of the Enterprise Search. Design and implementation of several applications following SOA principles using Angular.js and REST services. Design of several APIs to integrate legacy applications.\\}


\cventry{Apr 2012--Jun 2012}
{Data Architect}
{Online Guards}{UK}{}
{Redesign and implement their Big Data solution. My solution provided the same output reducing the processing time from 24h to 7 minutes.\\}

\cventry{Nov 2009--Oct 2010}
{Software Architect}
{Barcelona Council}{Spain}{}
{Advised the board of directors about Document Management strategy. Helped the Architecture Board to normalise the platform. Design frontend based on extJS to expose Documentum functionality. Code review and mentoring.\\}

\cventry{2008--2010}
{Architect}
{Toyota - Sword UK}{UK}{}
{Planned and designed the new Corporate Architecture based on Spring and other Open Source technologies. Assisted on the migration of the Portal and the Content Managemnt System. Code review and mentoring. Supervision of all the projects and procedures.\\}

\cventry{2006--2008}
{Architect}
{UBS }{UK}{}
{Technical design and specifications of a Credit Risk Platform. Technical team leadership.\\}

\cventry{2004--2006}
{Senior Technical Consultant}
{Sword UK, InSynCo AG,CSC}{UK}{}
{Consultant for clients like Common Wealth Secretariat, Bayer, BP, Antonio Puig, Aresa\\}


\cvline{}{}

\section{Side Projects}


\cvline{}{}

\cventry{2012--2013}
{:blibb}
{}{}{\url{blibb.net}}
{Content Management System with mobility and accessibility built into its core. Every single component of the CMS is exposed as a REST API, including the content.\\\\ :blibb is built using a different range of technologies: MongoDB, Python, ZeroMQ, PHP, Javascript, Redis.}

\cvline{}{}

\cventry{2013--2014}
{Oi!}
{}{}{\url{oioi.me}}
{Messaging platform that allows interchange pre-defined messages between groups of people.\\Built on :blibb. Mobile application (iOS and Android) and web client.}

\cvline{}{}

\cventry{Apr 2014--July 2016}
{dotMarks}
{}{}{\url{dotmarks.net/app/}}
{Self Hosted Bookmarks platform. REST API written in Python and Java with an angularjs web client and a google chrome extension. The system provides APIs and analytics.\\Python, Angular.js, Java, MongoDB, Cassandra, Celery, Docker.}

\cvline{}{}

%
% TECHS
%

\section{Technologies that I use regularly}
\cvline{}{
    \textbf{Go},
    J2EE, Maven,
    \textbf{PHP},
    \textbf{Python},
    Angular.js,
    \textbf{ZeroMQ},
    Docker,
    Nginx,
    \textbf{git},
    Javascript, grunt,
    Kafka,
    \textbf{flask},
    Vagrant,
    \LaTeX,
    CSS3,
    JaxB,
    REST Apis,
    SOA
}

\cvline{}{}


\cvline{}{}

%
% EDUCATION
%

\section{Education}
\subsection{Academic}
\cventry{1999--2004}
{Physics - DO}{University of Barcelona (Spain)}{}{}{}

\cvline{}{}

\subsection{Non academic}
\cventry{Nov 2014}
{Chef Fundamentals}{London (UK)}{}{}{}

\cventry{Nov 2014}
{Amazon Web Services - Big Data on AWS}{London (UK)}{}{}{}

\cventry{Jul 2014}
{ElasticSearch Core training}{London (UK)}{}{}{}

\cventry{Mar 2012}
{AWS Training Course}{Thoughtworks (UK)}{}{}{}

\cventry{Jul 2009}
{Spring Core Fundamentals}{Toyota (UK)}{}{}{}

\cventry{Jul 2009}
{Enterprise Integration with Spring}{Toyota (UK)}{}{}{}

\cventry{Jul 2009}
{Rich Web Applications with Spring}{Toyota (UK)}{}{}{}

\cventry{Apr 2008}
{Google Search Appliance}{Google Inc (UK)}{}{}{}
\cvline{}{}


%
% MISC
%

\section{Other resources}

\cvline{1}{My github:
\url{github.com/ipedrazas}}

\cvline{2}{Co-host of Kubecast, the Kubernetes podcast. \url{kubecast.com}}

\cvline{2}{Author of \url{k8s.uk}, a blog about kubernetes.}

\cvline{2}{Given talks in different meetups like the London kubernetes meetup,
microservices meetup, Hashicorp London meetup and, the London DevOps meetup.
Talks were mainly about using kubernetes in different scenarios}

\cvline{2}{Given a Kubernetes workshop in Jan 2016, Madrid.}

\cvline{2}{Given a talk ``Transforming the Government'' at Kubecon EU 2015.}

\cvline{2}{Given the workshop ``50 Shades of Docker'' at PyCon Spain 2014, agenda avilable at \url{2014.es.pycon.org/}.}

\cvline{2}{Given the workshop ``50 Shades of Big Data'' at PyCon Spain 2013, agenda avilable at \url{2013.es.pycon.org/}.}

\cvline{3}{Given a workshop about Mobile Development at Google Campus for the Queen Mary Entrepreneurs \url{www.qmsu.org/groups/qme/}.}

\cvline{4}{You can find more detailed information about my jobs on my LinkedIn
profile: \url{uk.linkedin.com/in/ivanpedrazas}.}

\cvline{5}{Blog: \url{ivan.pedrazas.me}.}

\end{document}
